Twists of supersymmetric gauge theories

### 2019-07-24 paper.tex
appendix

@@

\brian{can't do cokernels in CVS, blah blah}

There is a functor
\[
dif_c : \CVS \to \DVS .
\]

@@

@@

@@

@@

\begin{lemma} \label{invert_quis_lemma}
Any quasi-isomorphism of cochain complexes admits a quasi-inverse.
\end{lemma}
\brian{I think Pavel had something to say for this lemma.}

>>>>

\subsection{Differentiable vector spaces}
\def\Mfld{{\rm Mfld}}

Let $\Mfld$ denote the site of smooth manifolds (of arbitrary dimension) where the morphisms are smooth maps, and a cover $f : X \to Y$ is a surjective local diffeomorphism.

\begin{dfn} 
We use the following notations and naming conventions for sheaves on $\Mfld$:
\begin{itemize}
\item a {\bf smooth vector space} is a sheaf of vector spaces on $\Mfld$.
\item Let $C^\infty$ denote the smooth vector space which assigns the space of smooth functions $C^\infty(X)$ to a smooth manifold $X$.
\item a $C^\infty$-{\bf module} is a smooth vector space $V$ equipped with a structure of a module over $C^\infty$. 
If $V$ is a $C^\infty$-module, we denote $C^\infty(X, V) := V(X)$, the valued of $V$ on the smooth manifold $X$.
\item a {\bf differentiable vector space} is a $C^\infty$-module $V$ equipped with a flat connection
\[
\nabla_{X,V} : C^\infty(X, V) \to \Omega^1(X, V)
\]
for every smooth manifold $X$, which is required to be natural under pullbacks:
\[
f^* \circ \nabla_{Y,V} = \nabla_{X,V} \circ f^*
\]
for every smooth map $f : X \to Y$. 
A map of differentiable vector spaces is a map of $C^\infty$-modules which intertwines the flat connections. 
\end{itemize}
\end{dfn}

@@

There is a functor
\[
dif_c : \CVS \to \DVS 
\]
from the category of convenient vector spaces to the category of differentiable vector spaces. 
This functor does not preserve cokernels, so $dif_c$ does not preserve cohomology. 
In particular, with a naive definition of quasi-isomorphism internal to $\CVS$, the functor $dif_c$ does not preserve quasi-isomorphisms. 
To avoid this issue, we make the following definition.

@@

The cochain complexes arising in classical field theory are naturally convenient vector spaces. 
The above definition is used in what we mean by quasi-isomorphism between classical field theories, as in Definition \brian{??}.

Throughout the paper we make use of familiar manipulations with spectral sequences arising from filtrations of cochain complexes internal to differentiable vector spaces. 
A main tool is the classical Eilenberg-Moore comparison theorem, which is stated as follows.

The following is the natural definition of a filtered differentiable cochain complex.

@@

\subsubsection{The classical BV complex}

@@

The above lemma used the natural filtration on the classical BV complex given by polynomial degree of observables. 
Since the free part of the differential $Q$ always preserves this filtration, the first term of the resulting spectral sequence simply computes the cohomology of the underlying free theory. 
The differential on the higher pages depend on the interacting part of of the action.

@@

\begin{lemma} \label{invert_quis_lemma}
Any quasi-isomorphism of differentiable cochain complexes admits a quasi-inverse.
\end{lemma}
\brian{I think Pavel had something to say for this lemma.}
